Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*

### 2024-02-13 Code/ManuscriptTargetProtein.Rmd
Fixed x-axis order of Target proteins to represent biological process
Edits to ManuscriptTargetProtein.Rmd and Manuscript_O2.Rmd figure names and captions

```{r join deltaOD with chl DF}

@@

@@

MIT9313ProteinAttonated <- TargetProtein %>%
  filter( Strain == "MIT9313") %>% 
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.6, position = "stack", check_overlap = T), color = "Black") +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

MIT9313ProteinAttonated

MED4ProteinAttonated <- TargetProtein %>%
  filter( Strain == "MED4") %>% 
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

MED4ProteinAttonated
```

@@

 ggsave(file = file.path(PlotsOut, paste("MED4ProteinAttonated",".png",sep = "")), plot = MED4ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("MIT9313ProteinAttonated",".png",sep = "")), plot = MIT9313ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)

>>>>

```{r join protein data with culture meta data}

@@

```{r order protein by biological process}

TargetProtein  <- TargetProtein %>% 
 mutate(Target = factor(Target, levels = c("FtsH", "PsbA", "PetC", "PsaC", "RbcL")))

@@

MIT9313ProteinAnotated <- TargetProtein %>%
  filter( Strain == "MIT9313") %>% 
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.6, position = "stack", check_overlap = T), color = "Black") +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

MIT9313ProteinAnotated

MED4ProteinAnotated <- TargetProtein %>%
  filter( Strain == "MED4") %>% 
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

MED4ProteinAnotated
```

@@

 ggsave(file = file.path(PlotsOut, paste("MED4ProteinAnotated",".png",sep = "")), plot = MED4ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("MIT9313ProteinAnotated",".png",sep = "")), plot = MIT9313ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)

### 2024-02-13 Code/Manuscript_O2.Rmd
Edits to ManuscriptTargetProtein.Rmd and Manuscript_O2.Rmd figure names and captions

```{r ProchloroElectronTrans, fig.cap = ProchloroElectronTrans_cap , fig.height = 20, fig.width = 10, echo = FALSE}

ProchloroElectronTrans_cap <- glue("**Occurance of electron transport complexes data from the Ocean Protein Portal. X-axis is the oxygen concentration (µM) and the y-axis indicates the depth (m) of occurance**",
                       "Rows are...",
                       "Columns are...",

knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroElectronTrans.png"))
```

@@

MIT9313GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 grown under 660 nm (red) and 450 nm (blue) light.**",
                    "The x-axis is photoperiod (h).",
                    "The y-axis is actinic Photosynethetic Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
                    "**A.** represents the model under 250 µM of O~2~ and red light.",
                    "**B.** represents the model under 25 µM of O~2~ and red light.",
                    "**C.** represents the model under 2.5 µM of O~2~ and red light.",
                    "**D.** represents the model under 250 µM of O~2~ and blue light.",
                    "**E.** represents the model under 25 µM of O~2~ and blue light.",
                    "**F.** represents the model under 2.5 µM of O~2~ and blue light.",
                    "The legend represents a colour gradient of growth rate from no growth (white) to 1 d^-1^ (dark blue).",
                    "The labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",

@@

```{r ProchloroMetabDepthO2, fig.cap = ProchloroMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}

ProchloroMetabDepthO2_cap <- glue("**Protein turnover complexes data from the Ocean Protein Portal. The x-axis is the oxygen concentration (µM) and the y-axis indicates the depth (m) of occurance**",
                       "Rows are...",
                       "Columns are...",

@@

@@

```{r MED4ProteinAttonated, fig.cap = MED4ProteinAttonated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MED4ProteinAttonated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade).  **",

@@

knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAttonated.png"))
```

@@

```{r MIT9313ProteinAttonated, fig.cap = MIT9313ProteinAttonated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MIT9313ProteinAttonated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",

@@

knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAttonated.png"))
```

>>>>

```{r ProchloroPhotosynthDepthO2, fig.cap = ProchloroPhotosynthDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}

ProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
                       "Columns show detections of proteins annotated as from Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
                       "Horizontal lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
                       "Vertical lines indicate O~2~ (µM) used for  later culture growth.",
                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")

knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroPhotosynthDepthO2.png"))
```

@@

MIT9313GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 grown under 660 nm (red) and 450 nm (blue) light.**",
                    "The x-axis is photoperiod (h).",
                    "The y-axis is actinic Photosynthetically Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
                    "**A.** represents the model under 250 µM of O~2~ and red light.",
                    "**B.** represents the model under 25 µM of O~2~ and red light.",
                    "**C.** represents the model under 2.5 µM of O~2~ and red light.",
                    "**D.** represents the model under 250 µM of O~2~ and blue light.",
                    "**E.** represents the model under 25 µM of O~2~ and blue light.",
                    "**F.** represents the model under 2.5 µM of O~2~ and blue light.",
                    "The legend represents a colour gradient of growth rate from no growth (white) to 1 d^-1^ (dark blue).",
                    "The labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",

@@

```{r ProchloroProteinMetabDepthO2, fig.cap = ProchloroProteinMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}

ProchloroProteinMetabDepthO2_cap <- glue("**Protein turnover complexes data from the Ocean Protein Portal. The x-axis is the oxygen concentration (µM) and the y-axis indicates the depth (m) of occurance**",
                       "Rows are...",
                       "Columns are...",

@@

ProchloroElectronTrans_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein turnover complexes.**", 
                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
                       "Columns show detections of proteins annotated as from FtsH1, FtsH2, FtsH3 or Ribosome).",
                       "Horizontal lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
                       "Vertical lines indicate O~2~ (µM) used for  later culture growth.",
                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")

@@

```{r MED4ProteinAnotated, fig.cap = MED4ProteinAnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MED4ProteinAnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade).  **",

@@

knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAnotated.png"))
```

@@

```{r MIT9313ProteinAnotated, fig.cap = MIT9313ProteinAnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MIT9313ProteinAnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",

@@

knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAnotated.png"))
```
